UKB Models

### 2024-02-19 eda/ukb_curation-eda.Rmd
testing centile mods with euler

```{r}
ukb_df.ppt.qc <- ukb_df %>%
  dplyr::filter(participant %in% ppt.list)

@@

>>>>

```{r, eval=FALSE}
ukb_df.ppt.qc <- ukb_df %>%
  dplyr::filter(participant %in% ppt.list)

@@

##Exploratory QC

Adding euler number (from jakob) back into combat-ed dfs so i can test how controlling for euler in centile scores changes the performance of combat configs (esp. in CT based on Bedford et al preprint).

```{r}
cn.df_euler <- fread(paste0(base_path,"/data/lifespan_dataset_dkatlas_CNonly_euler.csv"), stringsAsFactors = TRUE)

ukb.df_euler <- cn.df_euler %>%
  dplyr::filter(study == "UKB") %>%
  dplyr::select(participant, surfholes)

table(unique(ukb_df_age.filt$participant) %in% unique(ukb.df_euler$participant)) #all subjects in df!

fwrite(ukb.df_euler, file=paste0(base_path,"data/ukb_euler_nums.csv"))
```
